\input{preamble}

\begin{document}
\section{KP22 - Algebraic reductions of knowledge}
$\bullet$ A difficulty from the lack of a unifying framework for ARK composition
is proving soundness, since each component of a complicated argument requires
its own soundness proof. Afterwards these piece-wise proofs must be shown
to ``add up to'' the soundness of the entire scheme, and this has been a
difficult task.

\medskip
$\bullet$ Public-coin setting, tree special soundness and its modularity consequences,
knowledge error= extractor's failure probability.

\medskip
$\bullet$ ``As a concrete example, we show that an argument for NP can be modularly
implemented in our framework by using both sequential and parallel composition''.

\medskip
$\bullet$ Tree special soundess implies their notion of soundness.

\medskip
$\bullet$ Recursive ARGUMENTS over Homomorphic structures (say rings) $\to$
Tensor REDUCTION of KNOWLEDGE.

\medskip
$\bullet$ Leverage homomorphic structure to improve both asymptotics and concrete
efficiency.

\medskip
$\bullet$ Tensor reduction: information-theoretic protocol.

\medskip
$\bullet$ Sum-check protocol : ARKs $\leftrightarrow$ Tensor reduction : RoKs.

\medskip
$\bullet$ Reduction= (completeness1, soundness1) $\to$ (completeness2, soundness2)

\medskip
$\bullet$ \textbf{Sampling set.}
Let $M$ be an $R$-module. Then $Q \subset R$ is a \emph{sampling set} for
$M$ if for any two $q_1, q_2 \in Q$ the map
\[
	\begin{array}{c}
		\phi: M \to M\\
		m \mapsto (q_1 - q_2)m
	\end{array}
\]
is injective.

\medskip
$\bullet$ \textbf{Coset equality assumption.} Given $u_1, \ldots, u_n$ and
$v_1, \ldots, v_n$ there exists a polynomial time algorithm to check
\[
	\sum_{i \in [n]} u_i\otimes v_i = 0.
\]

\medskip
$\bullet$ **Where in the paper will they non-trivially assume the coset equality
assumption?**

\medskip
$\bullet$ \textbf{Public reducibility.} The verifier's output statement $u_2$
can be deterministically recovered from the public parameters, input statement
$u_1$ and the interaction transcript.

\section{KST21 - Nova}
$\bullet$ Nova is non-interactive

\medskip
$\bullet$ ...Next comment...
\end{document}
